---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![Travis-CI Build Status](https://travis-ci.org/hypertidy/scspatstat.svg?branch=master)](https://travis-ci.org/hypertidy/scspatstat)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/hypertidy/scspatstat?branch=master&svg=true)](https://ci.appveyor.com/project/hypertidy/scspatstat)
[![Coverage Status](https://img.shields.io/codecov/c/github/hypertidy/scspatstat/master.svg)](https://codecov.io/github/hypertidy/scspatstat?branch=master)



```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# scspatstat

The goal of `scspatstat` is to convert `spatstat` data structures to a generic common form that that can be used for conversion a wide variety of data structures.

This is work in progress and at a very early stage. More to come.


## Example

This is a basic example showing the component decomposition of a spatstat point pattern. 

```{r example}
library(scspatstat)
library(dplyr)
data("chorley", package = "spatstat.data")
sc_object(chorley) %>% slice(2L)

data("nbfires", package= "spatstat.data")
sc_path(spatstat::as.owin(nbfires))

print(sc_coord(spatstat::as.owin(nbfires)), n = 5)


```

With these three components working `sc_coord`, `sc_object` and `sc_path`, and using the framework in `sc`,  the parent package can use these *in generic form*. We can already convert to `PATH` and then on to other models for these polygonal forms in `spatstat`.

```{r}
library(scspatstat)
str(nbfires_path <- silicate::PATH(spatstat::as.owin(nbfires)))

SC(nbfires_path)
```

(Note that `owin` is supported only on its own, and points `ppp` and line segments `psp` are supported separately. We need a way to intermingle structured "windows" and the underlying patterns, but for now I consider that a higher specialization that silicate itself. 


Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
